\begin{thebibliography}{1}
\bibitem{MechanicalFeedback} Buchmann, A. Alber, M., Zartman, J. \emph{ Sizing it up: The mechanical feedback hypothesis of organ growth regulation.} Seminars in Cell and Developmental Biology, 2014.
\bibitem{Chaste Tutorial} \emph{Chaste Tutorial} \url{https://chaste.cs.ox.ac.uk/chaste/tutorials/release_2.1/UserTutorials.html}
\bibitem{Drasdo} Drasdo, D. \emph{Bucking Instabilities of One Layered Growing Tissues.} Physical Review Letters 84.
\bibitem{Epithelium}\emph{Epithelial Tissues} \url{http://www.botany.uwc.ac.za/sci_ed/grade10/mammal/epithelial.htm}
\bibitem{Vertex Models} Fletcher, A. , Osterfield, M., Baker, R., Shvartsman, S. \emph{Vertex Models of E[ithelial Morphogenesis.} Biophysical Journal 106, June 2014.
\bibitem{ChasteMain} Fletcher, A., Osborne, J., Maini, P, Gavaghan, D. \emph{Implementing vertex dynamics models of cell populations in biology within a consitent computational framework.} Prog. Biophys. Mol. Biol. 113: 299 - 326.
\bibitem{Overview} Gibson, W., Gibson, M. \emph{Cell Topology, Geometry, and Morphogenesis  in Proliferating Epithelia.} Current Topics in Developmental Biology 89.
\bibitem{Soap} Weaire, D. and Rivier, N. \emph{Soap, Cells, and Statistics}
\bibitem{Udacity} Luebke, D. and Owens, J. \emph{Intro to Parallel Programming} \url{https://www.udacity.com/course/cs344} 2013.
\bibitem{HondaNagai} Nagai, T. Honda, H. \emph{A dynamic model for the formation of epithelial tissues.} Philisohpical Magazine, Pt. B. Vol 81, Issue 7, 2001.
\bibitem{Morphogen} Restrepo, S., Zartman, J. , and Basler, K. \emph{ Coordination of Patterning and Growth by the Morphogen DPP} Current Biology 24, 245- 255.

\end{thebibliography}